On the link between functional traits and growth rate: meta-analysis shows effects change with plant size, as predicted

### 2016-03-07 MS.tex
Changes some sentences in the result part to better fit with the cover letter

For wood density and seed mass the available results are consistent with expectation from theory but it would be desirable to have substantially more data. Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).

>>>>

For wood density and seed mass, the available results are consistent with expectation from theory but it would be desirable to have substantially more data. Indeed, while meta-analysis is possible even with few observations, strong conclusions are generally precluded by very large CIs of the effect size (i.e highly uncertain estimates and CI often spanned zero).
